Um modelo de suporte distribuído para jogos MMOG em cenários com recursos computacionais limitados

### 2009-09-01 textos/PlanoDoutorado/planodoc_lugano.tex

>>>>

As mentioned in the previous section, MMOGs are characterized by a large number of players. To support this great number of participants, a client-server infrastructure is generally used, and all interaction is done through the server machine. In this paradigm, the server computer has the official copy of the game state and it is responsible for computing its change over time, while the game client is responsible for presenting to the user the game state sent by the server. The server is also responsible for updating the clients, in real time, on the changes that occur in the virtual environment of the game. Because of the high number of participants, the centralization on the game server makes the maintanance cost very high. Generally, it is required a connection to the Internet with several GBps of bandwidth and enough processing power to run the simulation of the virtual world \cite{feng2007wnn}. It becomes impossible, for example, the maintenance of massively multiplayer online games by small or independent groups on a limited budget.
